Parallel Quadtree Construction on Collections of Objects

### 2017-05-06 paper.tex
added discussion of the use of an atomic for propagating brt colors for pruning

We then propagate the BRT labels up the tree in parallel, marking ``unknown'' nodes as ``required'' when the labels of the current node's two child nodes don't match. Finally, we generate quadtree nodes from only the required internal binary radix tree nodes.

>>>>

We then propagate the BRT labels up the tree in parallel, marking ``unknown'' nodes as ``required'' when the labels of the current node's two child nodes don't match. \blue{Labels are applied using an atomic compare and swap, and threads terminate if the current ancestor's label was previously ``unknown''.} Finally, we generate quadtree nodes from only the required internal binary radix tree nodes.
